---
title: "group_03_package"
output: rmarkdown::pdf_document
vignette: >
  %\VignetteIndexEntry{group_03_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Lab8Package)
```

The package "group 3" is a simple DNA/RNA sequence tool. 
Link to our GitHub repository: https://github.com/rforbiodatascience25/group_03_package

This package provides a small collection of functions for generating, manipulating, and analyzing nucleotide and amino acid sequences. It allows users to create random DNA sequences, transcribe DNA to RNA, split sequences into codons, translate codons into amino acid sequences, and visualize amino acid composition as bar plots.

Function 1 : random_dna1

This function creates a synthetic DNA sequence of a specified length, given as an input. It randomly samples nucleotides from the standard DNA bases (adenine, thymine, guanine, and cytosine) with replacement, then concatenates them into a single continuous string.

```{r}
#variable inside function, called random_dna2, is the input by the user. This should be the desired lenght of DNA
random_dna1 <- function(random_dna2){
  random_dna3 <- sample(c("A", "T", "G", "C"), size = random_dna2, replace = TRUE)
  #random_dna3 generates the random dna-like sequence with the size given in random_dna2
  random_dna4 <- paste0(random_dna3, collapse = "")
  #in random_dna4 is the random sequence generated but converting it into a string, without any spaces in between.
  return(random_dna4)
  }
```



Use cases for this package: 
This package is a DNA/RNA/protein sequence toolkit. Then it could be use for teaching and learning molecular biology concepts, for a quick demostration on how the central dogma of biology works. Moreover, it is useful for bioinformatics pipelines, for example, for generating synthetic DNA sequences for testing sequence-processing algorithms or simulating codon usage in silico.

Besides the five functions included in this package, we could provide more functions to make it more versatile. For example: 

- Reverse complement
- Calculation of the GC content
- Translate RNA/DNA with Codon Table for specific microorganisms
- Sequence Validation in case there is an invalid character

Everyone writes about their function and some code for explanation 


about and demonstrate how each function in the package is used (individually and in conjunction with each other). 
 





Function 2:

This function takes a DNA sequence in argument and returns the corresponding RNA sequence. The process that is realized is changing the "T" into "U".
For instance, the "ATTGCT" DNA sequence will be converted into "AUUGCU".

```{r}
convert_T_U("ATTGCT")
```

In our process, we will use the random DNA sequence created with function 1 and make it an RNA one.


Function 4:

This function "codons_into_aa" uses the data table we integrated. The "data_codon.rda" table links the trios of codons to the corresponding amino-acid.
For instance, the codon ("UUU", "GAC", "AAG") will become "FDK" after going through the function.

```{r}
codons <- c("UUU", "GAC", "AAG")
codons_into_aa(codons)
```
In our process, we use the sequence randomly generated that previously had been groupped in trios with function 3 and we translate it into amino-acids.
